Paper notes

### 2019-08-28 paper_notes.Rmd
Add files via upload

  f_eth <- function(i_e,M,x,n,S){
   if (x > n){
     U <- NA}else{
     if (x < round(n*i_e,digits = 2)){
   U <- (x / round((n*i_e),digits = 2)) * S
      }else if (x > round((n*i_e),digits = 2)){
         U <- M + ((1- (x/n))*(1-M))/(1-i_e) 
        }else{
     U <- 1}
        round(U,digits = 3)
      }
 }

@@

f_val <- function(e_w,ew_ng,M,i_v,S){
  if (round(abs(e_w-ew_ng), digits=2) <= i_v) {
    U <- 1
    }else{
      U <- (M + ((1-(round(abs(e_w-ew_ng), digits=2)))*(1-M))/(1-i_v)) * S
      }
  round(U,digits = 3)
  }

@@

#prob <- function(d_u_e,d_u_v,e_w,v_w,k){round(1 / (1 + exp((-(e_w*k)*(d_u_e)) + (-(v_w*k)*(d_u_v)))),digits= 2)}
prob <- function(d_u_e,d_u_v,e_w,v_w,k){1 / (1 + exp((-(e_w*k)*(d_u_e)) + (-(v_w*k)*(d_u_v))))}

@@

$$
U^i_v=
\begin{cases}
1, & \text{if} \ \mid{\overline{ew}_j - ew_i}\mid \leq i_v, \\
\\
\left(M + \frac{(1 - \mid{\overline{ew}_j - ew_i}\mid) \times (1 - M)}{1 - i_v}\right) \times S, & otherwise
\end{cases}
$$

@@

e_w <- 0.2
e_w_ng <- seq(0.0,1.0, by = 0.1)
i_v <- 0.1
S <- 1
M <- 0

fvf0p  <- f_val(e_w,0,M,i_v,S)
fvf1p  <- f_val(e_w,0.1,M,i_v,S)
fvf2p   <- f_val(e_w,0.2,M,i_v,S)
fvf3p   <- f_val(e_w,0.3,M,i_v,S)
fvf4p   <- f_val(e_w,0.4,M,i_v,S)
fvf5p   <- f_val(e_w,0.5,M,i_v,S)
fvf6p   <- f_val(e_w,0.6,M,i_v,S)
fvf7p   <- f_val(e_w,0.7,M,i_v,S)
fvf8p   <- f_val(e_w,0.8,M,i_v,S)
fvf9p  <- f_val(e_w,0.9,M,i_v,S)
fvf10p  <- f_val(e_w,1.0,M,i_v,S)

e_w <- 0.2
e_w_ng <- seq(0.0,1.0, by = 0.1)
i_v <- 0.1
S <- 0
M <- 0

fvf0t <- f_val(e_w,0,M,i_v,S)
fvf1t  <- f_val(e_w,0.1,M,i_v,S)
fvf2t   <- f_val(e_w,0.2,M,i_v,S)
fvf3t   <- f_val(e_w,0.3,M,i_v,S)
fvf4t   <- f_val(e_w,0.4,M,i_v,S)
fvf5t   <- f_val(e_w,0.5,M,i_v,S)
fvf6t  <- f_val(e_w,0.6,M,i_v,S)
fvf7t   <- f_val(e_w,0.7,M,i_v,S)
fvf8t   <- f_val(e_w,0.8,M,i_v,S)
fvf9t  <- f_val(e_w,0.9,M,i_v,S)
fvf10t  <- f_val(e_w,1.0,M,i_v,S)

@@

$P_j=\frac{1}{1 + \exp((-\beta_e{(e_j-e_i)}) + (-\beta_v{(v_j-v_i)}) }$

@@

$P_j=\frac{1}{1 + \exp((-\beta_e(ej-ei)) + (-\beta_v(vj-vi)))$

@@

i_e = 0.5   # parameters to manipulate
S = 1     # Symmetric single-peaked function: S=1,M=0
M = 0     # Linear + Constant function = S=1,M=1
n = 8     # Schelling Threshold function = S=0,M=1

@@

e_w <- 0.4    # parameters to manipulate
i_v <- 0.2    # Symmetric = S:1,M:0/Threshold = S:0
S  <- 1
M <-  0

fv0d2 <- f_val(e_w,0,M,i_v,S)             # value utility for each option, 
fv1d2 <- f_val(e_w,0.1,M,i_v,S)           # increasing number is average ethnic weight of neighborhood j
fv2d2 <- f_val(e_w,0.2,M,i_v,S)
fv3d2 <- f_val(e_w,0.3,M,i_v,S)
fv4d2 <- f_val(e_w,0.4,M,i_v,S)
fv5d2 <- f_val(e_w,0.5,M,i_v,S)
fv6d2 <- f_val(e_w,0.6,M,i_v,S)
fv7d2 <- f_val(e_w,0.7,M,i_v,S)
fv8d2 <- f_val(e_w,0.8,M,i_v,S)
fv9d2 <- f_val(e_w,0.9,M,i_v,S)
fv10d2 <- f_val(e_w,1.0,M,i_v,S)

@@

report_V <- na.omit(data.frame(M,S,des_dist,ew_agent,mean_ew_ng,Utility_V))

title_cond_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"\n\r","M =", M,"; ", "S = ",S)

>>>>

  f_eth <- function(i_e,M,x,n,S){
   if (x > n){
     U <- NA}else{
     if (x < (n*i_e)){
   U <- (x / (n*i_e)) * S
      }else if (x > (n*i_e)){
         U <- M + ((1- (x/n))*(1-M))/(1-i_e) 
        }else{
     U <- 1}
        round(U,digits = 3)
      }
 }

@@

f_val <- function(e_w,ew_ng,M,i_v,S_v){
  if (round(abs(e_w-ew_ng), digits=2) <= i_v) {
    U <- 1
    }else{
      U <- (M + ((1-(round(abs(e_w-ew_ng), digits=2)))*(1-M))/(1-i_v)) * S_v
      }
  round(U,digits = 3)
  }

@@

prob <- function(d_u_e,d_u_v,e_w,v_w,k){round(1 / (1 + exp((-(e_w*k)*(d_u_e)) + (-(v_w*k)*(d_u_v)))),digits= 2)}
# prob <- function(d_u_e,d_u_v,e_w,v_w,k){1 / (1 + exp((-(e_w*k)*(d_u_e)) + (-(v_w*k)*(d_u_v))))}

@@

$$
U^i_v=
\begin{cases}
1, & \text{if} \ \mid{\overline{ew}_j - ew_i}\mid \leq i_v, \\
\\
\left(M + \frac{(1 - \mid{\overline{ew}_j - ew_i}\mid) \times (1 - M)}{1 - i_v}\right) \times S_v, & otherwise
\end{cases}
$$

@@

e_w <- 0.2
e_w_ng <- seq(0.0,1.0, by = 0.1)
i_v <- 0.1
S_v <- 1
M <- 1

fvf0p  <- f_val(e_w,0,M,i_v,S_v)
fvf1p  <- f_val(e_w,0.1,M,i_v,S_v)
fvf2p   <- f_val(e_w,0.2,M,i_v,S_v)
fvf3p   <- f_val(e_w,0.3,M,i_v,S_v)
fvf4p   <- f_val(e_w,0.4,M,i_v,S_v)
fvf5p   <- f_val(e_w,0.5,M,i_v,S_v)
fvf6p   <- f_val(e_w,0.6,M,i_v,S_v)
fvf7p   <- f_val(e_w,0.7,M,i_v,S_v)
fvf8p   <- f_val(e_w,0.8,M,i_v,S_v)
fvf9p  <- f_val(e_w,0.9,M,i_v,S_v)
fvf10p  <- f_val(e_w,1.0,M,i_v,S_v)

e_w <- 0.2
e_w_ng <- seq(0.0,1.0, by = 0.1)
i_v <- 0.1
S_v <- 0
M <- 0

fvf0t <- f_val(e_w,0,M,i_v,S_v)
fvf1t  <- f_val(e_w,0.1,M,i_v,S_v)
fvf2t   <- f_val(e_w,0.2,M,i_v,S_v)
fvf3t   <- f_val(e_w,0.3,M,i_v,S_v)
fvf4t   <- f_val(e_w,0.4,M,i_v,S_v)
fvf5t   <- f_val(e_w,0.5,M,i_v,S_v)
fvf6t  <- f_val(e_w,0.6,M,i_v,S_v)
fvf7t   <- f_val(e_w,0.7,M,i_v,S_v)
fvf8t   <- f_val(e_w,0.8,M,i_v,S_v)
fvf9t  <- f_val(e_w,0.9,M,i_v,S_v)
fvf10t  <- f_val(e_w,1.0,M,i_v,S_v)

@@

$P_j=\frac{1}{1 + \exp((-\beta_e{(e_j-e_i)}) + (-\beta_v{(v_j-v_i)})}$

@@

$P_j=\frac{1}{1 + \exp((-\beta_e(ej-ei)) + (-\beta_v(vj-vi)))}$

@@

i_e = 0.6   # parameters to manipulate
S = 1     # Symmetric single-peaked function: S=1,M=0
M = 0     # Linear + Constant function = S=1,M=1
n = 8     # Schelling Threshold function = S=0,M=1

@@

e_w <- 0.5    # parameters to manipulate
i_v <- 0.2    # Symmetric = S:1,M:0/Threshold = S:0
S_v  <- 0
M <-  0

fv0d2 <- f_val(e_w,0,M,i_v,S_v)             # value utility for each option, 
fv1d2 <- f_val(e_w,0.1,M,i_v,S_v)           # increasing nuMber is average ethnic weight of neighborhood j
fv2d2 <- f_val(e_w,0.2,M,i_v,S_v)
fv3d2 <- f_val(e_w,0.3,M,i_v,S_v)
fv4d2 <- f_val(e_w,0.4,M,i_v,S_v)
fv5d2 <- f_val(e_w,0.5,M,i_v,S_v)
fv6d2 <- f_val(e_w,0.6,M,i_v,S_v)
fv7d2 <- f_val(e_w,0.7,M,i_v,S_v)
fv8d2 <- f_val(e_w,0.8,M,i_v,S_v)
fv9d2 <- f_val(e_w,0.9,M,i_v,S_v)
fv10d2 <- f_val(e_w,1.0,M,i_v,S_v)

@@

report_V <- na.omit(data.frame(M,S_v,des_dist,ew_agent,mean_ew_ng,Utility_V))

title_cond_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"\n\r","M =", M,"; ", "S = ",S_v)
